### 2021-09-06 input/proposal.tex
wining space piece by piece

To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a \process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure.  This
section describes the communication primitive called scoped broadcast,
then discusses the properties that guarantee consistent partitioning
in our context, and finally details our implementation \NAME and the
analysis of its complexity.

@@

% \TODO{dynamic graph: superscript with $t$?}
In this paper, we consider Edge infrastructures with heterogeneous
\nodes interconnected by communication links. \Processes involved in
the management of content may crash but are not byzantine.  Finally,
\processes can reliably communicate through asynchronous message
passing to other known \processes called neighbors.  % A more formal
%definition of our system is given below:

@@

We define scoped broadcast as a communication primitive that
propagates a message around its broadcaster within an
application-dependant scope:

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that epidemic propagation and scoped broadcast have
well-aligned preoccupations. More precisely, it underlines the transitive relevance of
messages, thus \processes can stop forwarding messages as soon as the
corresponding predicate becomes unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.
%
We use \NAMEB to dynamically and efficiently modify the state of each
\process depending on all partitions that exist in the system.

@@

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_X$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_X$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_X$:] \Processes such as
    \Process~$a$ where the last and best partition is still $P_X$. By
    propagating from \process to \process the corresponding $\delta_X$
    message, these \processes purge $\alpha_X$.
  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
    \Process~$b$ that do not directly suffer from the non-delivery of
    $\delta_X$. They need to purge their own $P_Y$ if need
    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
    one following \process will receive.
  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
    such as \Process~$c$ that do not belong to the preceding category,
    for they already delivered $\delta_Y$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_Y$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_X$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_X$ to emphasize
    their relative similarity to $\delta_X$ messages.
    % the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
    their parent:] \Processes such as \Process~$d$ that have
    $\alpha_X$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_X$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

  Propagation~I terminates: a \process does not deliver a $\delta$
  message if it has already delivered it. Propagation~III terminates: a
  \process does not deliver a looping message.
  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  These three phases propagation-detection-propagation ensure that
  \processes eventually purge stale $\alpha$ messages from the system,
  leaving room for Propagation~I.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

@@

\begin{algorithm}[h!]
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$ in static networks.}
\end{algorithm}

@@

\begin{algorithm}[h!]
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

Algorithm~\ref{algo:edges} extends \NAME to enable dynamic consistent
partitioning in dynamic networks where \processes can join or leave
the system without notification. We consider that removing a \process
is equivalent to removing all its edges, and adding a \process is
equivalent to add as many edges as necessary.

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the shortest
path of one of involved \processes plus downstream \processes. As a
side effect, removing an edge may also impair the propagation of a
partition delete. To implement this behavior, \NAME uses its
implementation of $\Delta$ messages. This prove costly but enables
\NAME even in dynamic networks subject to physical partitioning.

>>>>

To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a \process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure.  This
section describes the communication primitive called scoped broadcast,
then discusses the properties that guarantee consistent partitioning,
and finally details our implementation \NAME.
% and the analysis of its complexity.

@@

% \TODO{dynamic graph: superscript with $t$?}
In this paper, we consider Edge infrastructures with heterogeneous
\nodes interconnected by communication links. \Processes involved in
the management of content may crash but are not byzantine.  \Processes
can reliably communicate through asynchronous message passing to other
known \processes called neighbors.  % A more formal
%definition of our system is given below:
We define scoped broadcast as a communication primitive that
propagates a message around its broadcaster within an
application-dependant scope.

@@

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that epidemic propagation and scoped broadcast have
well-aligned preoccupations. More precisely, it underlines the
transitive relevance of messages, thus a \process can stop forwarding
messages as soon as its predicate becomes unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.
%
We use \NAMEB to efficiently modify the state of each \process
depending on the partitions that exist in the system.

@@

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_X$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_X$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_X$:] \Processes such as $a$
    where the last and best partition is still $P_X$. By propagating
    from \process to \process the corresponding $\delta_X$ message,
    these \processes purge $\alpha_X$.
  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
    \Process~$b$ that do not directly suffer from the non-delivery of
    $\delta_X$. They need to purge their own $P_Y$ if need
    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
    one following \process will receive.
  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
    such as \Process~$c$ that do not belong to the preceding category,
    for they already delivered $\delta_Y$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_Y$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_X$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_X$ to emphasize
    their proximity to $\delta_X$ messages.
    % the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
    their parent:] \Processes such as \Process~$d$ that have
    $\alpha_X$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_X$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

  Propagation~I terminates: a \process does not deliver a $\delta$
  message if it has already delivered it. Propagation~III terminates: a
  \process does not deliver a looping message.
  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  These three phases propagation-detection-propagation ensure that
  \processes eventually purge stale $\alpha$ messages from the system,
  leaving room for best eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

@@

\begin{algorithm}[h!]
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

@@

%% \begin{algorithm}[h!]
%%   \input{input/algoedges.tex}
%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
%% \end{algorithm}

Algorithm~\ref{algo:ascast} also enables dynamic consistent
partitioning in dynamic networks where \processes can join, leave, or
crash at any time. Removing a \process is equivalent to removing all
its edges, and adding a \process is equivalent to add as many edges as
necessary.  Adding an edge between two \processes may only improve the
shortest path of one of these \processes. Therefore, it triggers a
competition between the two \processes only. If one or the other
\process improves, the propagation of $\alpha$ messages operates
normally.  Removing an edge between two \processes may invalidate the
shortest path of one of involved \processes plus downstream
\processes. As a side effect, removing an edge may also impair the
propagation of a partition delete. To implement this behavior, \NAME
uses its implementation of $\Delta$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.
